---
title: "Welcome to 5523 blog"
description: |
  Welcome to 5523 assignment blog.
author:
  - name: DIYAO CHEN 
    
date: 09-01-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE,echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r library, include=FALSE,echo = FALSE}
library(dplyr)
library(tidyverse)
library(readr)
library(kableExtra)
library(ggplot2)
library(plotly)
library(coronavirus)
library(lubridate)
```



# Introduction
Coronavirus disease 2019 (COVID‑19) is an infectious disease caused by severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2).It was first identified in December 2019 in Wuhan, Hubei, China, and has resulted in an ongoing pandemic. As of 31 August 2020, more than 25.3 million cases have been reported across 188 countries and territories, resulting in more than 848,000 deaths. More than 16.6 million people have recovered(wikipedia)

In this blog, we will focus on the covid19 in France.

# Data description
The dataset used for this analsis was retrieved from [coronavirus](https://github.com/RamiKrispin/coronavirus)The coronavirus package provides a tidy format dataset of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) epidemic. The raw data pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository. which to analysis the case of covid19 in 2019

```{r data description}

colnames(coronavirus)%>%
kable() %>%
    kable_styling(bootstrap_options = c("striped"))

```
There are 7 vars and 174271 obs in the dataset.
The var explain:
date - The date of the summary
province - The province or state, when applicable
country - The country or region name
lat - Latitude point
long - Longitude point
type - the type of case 
cases - the number of daily cases 


# Data analysis
```{r data analysis, echo = FALSE,warning=FALSE,message=FALSE}
dat <- coronavirus%>%
  filter(country == "France")%>%
  mutate(month=month(date))%>%
  group_by(month,type)%>%
  summarise(total = sum(cases))%>%
   pivot_wider(names_from = type,
              values_from = total)%>%
  mutate(death_rate = round(death/confirmed*100))%>%
  mutate(recovered_rate=round(recovered/confirmed*100))
  

```


```{r}
DT::datatable(dat, options = list(pageLength = 7))

```