---
title: "Welcome to 5523 blog"
description: |
  Welcome to 5523 assignment blog.
author:
  - name: DIYAO CHEN 
    
date: 09-01-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE,echo = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r library, include=FALSE,echo = FALSE}
library(dplyr)
library(tidyverse)
library(readr)
library(kableExtra)
library(visdat)
library(tidytext)
library(ggplot2)
library(wordcloud)
library(plotly)
library(coronavirus)
```

```{r read data, echo = FALSE}
covid19 <- read_csv(here::here("Data/covid19.csv"))
head(covid19)
```



# Introduction

# Data description
The dataset used for this analsis was retrieved from [coronavirus](https://github.com/RamiKrispin/coronavirus)The coronavirus package provides a tidy format dataset of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) epidemic. The raw data pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository. which to analysis the case of covid19 in 2019

```{r data description}

colnames(covid19)%>%
kable() %>%
    kable_styling(bootstrap_options = c("striped"))

```
There are 9 vars and 174271 obs in the dataset.
The var explain:
date - The date of the summary
province - The province or state, when applicable
country - The country or region name
lat - Latitude point
long - Longitude point
type - the type of case 
cases - the number of daily cases 




```{r data analysis, echo = FALSE}
France <- covid19 %>% 
  filter(location == "France") %>%
  
print(France)
 
```


